\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

The continuous growth of the data in the hands of the companies has always
presented a real problem to manage it, a problem that has been tackled by Talend
by developing and delivering its product
\href{https://www.talend.com/products/data-inventory/}{Data Inventory} offering
a set of functionalities to its clients. In order to increase the capabilities
of this tool, the Talend Lab team proposes to work on a research project aiming
to at extracting metadata from the data allowing to easily detect similarities
between datasets. 

It is in this context that the present project takes place, where we explore the
literature related to dataset similarity detection and implement techniques to
efficiently extract metadata from any new dataset. We built during this project
a proof of concept that provides the user with the possibility to introduce and
index a new dataset, and to compute efficiently for a selected dataset, the
degree of similarity with the other dataset in the system. We scaled the
similarity detection from the level of datasets to the level of their columns
and we used the latter to deduce a score for the first.

This type of functionality can be used in different ways, we can use it suggest
to the user to compare and merge two similar datasets, or to update the records
of one of them. We can also use it to detect the topic of the dataset if the
ones similar to it have already been tagged with their respective topics.

To build our solution, we tackle this topic as \acrfull{nns} problem, and we use
a method from the \acrfull{lsh} family which is Cross-Polytope LSH and we
combine it with Multi-Probe LSH to improve its indexation quality. This solution
has been tested on a benchmark that has been used in an internal project at
Talend, and it shows up that our solution achieves an accuracy of 60\% when it
comes to reproduce human-labelled similarities.

\vspace{2cm}
\textbf{Keywords:}
\acrlong{nns}, \acrlong{lsh}, Cross-Polytope, Data Fingerprinting, Indexation,
Similarity \& Dissimilarity Metrics