\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement and Dedication}
\thispagestyle{empty}


\vspace{0.75cm}
\textit{This thesis was made possible thanks to the help of several people to whom I would like to express my gratitude.}
\vspace{0.75cm}

\textit{ First of all, I would like to thank my two supervisors in this work, Mr. Pedro Fillastre and Mr. Jean-Marc Brun. They were there when I needed answers, suggestions, advice and reviews that helped me to improve the quality of my work. I am grateful to them for their constant presence, their constructive criticism and their considerable efforts.}

\vspace{0.75cm}

\textit{I would also like to thank my supervisor Mr. Mohamed Nadif and the person in charge of training, for his immense help, as well as for all the advice and information he gave us with a degree of patience and professionalism throughout my course at the university.}
\vspace{0.75cm}


\textit{I would also like to express my sincere thanks to Mr. Sebastiao Correia, the manager of the Lab team at Talend, for offering me the opportunity to join the team, for his support, his guidance, his availability and his constant presence during this internship period.}
\vspace{0.75cm}


\textit{I would also like to thank everyone at Suresnes offices who welcomed me and made my integration easier, and especially the members of the Lab team for their opinions and constructive criticism.}
\vspace{0.75cm}


\textit{I would also like to thank the members of the jury who took the time to review and evaluate my work in the best possible way.}

